A Sound and Complete Deep Embedding of Arbitrary Normal Modal Logics in Coq

### 2025-08-20 paper/COLA/paper.tex
Add minor comment
Clarify change from SBLP

This article is an extended version of our SBLP 2022 work~\cite{Silveira22}. In this paper we also include
a detailed discussion about our formalization of a completeness proof for the Hilbert-style deductive
system following the strategies found in traditional modal logic books~\cite{Blackburn-ModalLogics}.
The rest of this work is organized as follows: Section~\ref{sec:background} provides
brief introduction on modal logics and the Coq proof assistant. Details about
the implementation of our Coq library are presented in
Section~\ref{sec:implementation}. A case study in proving L\"ob's theorem is
the subject of Section~\ref{sec:case}. Related works are discussed
on Section~\ref{sec:related} and Section~\ref{sec:conclusion} draws some conclusions and
provide some pointers for future work.
%
All source code in this article has been formalized in Coq version 8.15 and
is available at \url{https://github.com/funcao/LML/} under a permissive free software license.

@@

\noindent We can now write down L\"ob's theorem as follows:

>>>>

This article is an extended version of our SBLP 2022 work~\cite{Silveira22}. In this paper we also include
a detailed discussion about our formalization of a completeness proof for the Hilbert-style deductive
system following the strategies found in traditional modal logic books~\cite{Blackburn-ModalLogics,Popkorn_1994},
which was not present in the earlier version of the paper.
The rest of this work is organized as follows: Section~\ref{sec:background} provides
brief introduction on modal logics and the Coq proof assistant. Details about
the implementation of our Coq library are presented in
Section~\ref{sec:implementation}. A case study in proving L\"ob's theorem is
the subject of Section~\ref{sec:case}. Related works are discussed
on Section~\ref{sec:related} and Section~\ref{sec:conclusion} draws some conclusions and
provide some pointers for future work.
%
All source code in this article has been formalized in Coq version 8.15 and
is available at \url{https://github.com/funcao/LML/} under a permissive free software license.

@@

\noindent We can now write down L\"ob's theorem as follows (representing the axiom through derivations):
